MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
fixed related work section

@@

Vulnerabilities: 
"Device authentication is simple shared-key challenge/response." \cite{scarfone2008guide}

@@

\section{Related Work}
%not sure this section is really necessary because of the last section
Phan and Mingard show that a malicious device can impersonate a legitimate device and communicate with another legitimate device by making the user enter whichever authentication pin it chooses \cite{phan2012analyzing}.

BT-Nino-MITM: Bluetooth No Input, No Output 
MITM forcing devices into Just Works mode \cite{4401672}

Public key management is a problem \cite{almonanimitmssp}
theoretical man-in-the-middle attack on the Bluetooth Passkey Entry method \cite{barnickel2012implementing}

The most relevant research to our own Basic BT attack on keyboard \cite{cuthbertbluetooth}
\section{Threat Model}
TODO

@@

>>>>

Public key management is a problem \cite{almonanimitmssp}

@@

@@

\section{Related Work}
MITM attacks are commonly researched for Bluetooth technologies and there are a variety of approaches to executing the attacks. As previously mentioned, the PIN prevents potential issues and is vulnerable to social engineering attacks. Phan and Mingard show that a malicious device can impersonate a legitimate device and communicate with another legitimate device by making the user enter whichever authentication pin it chooses \cite{phan2012analyzing}. Other approaches target reused pins by eavesdropping on the pairing process, jamming the signal, and then attempting to pair to the devices using the already-used pin \cite{barnickel2012implementing}. These approaches rely on the victim not thinking critically about the pin -- in some cases, the pin is hard-coded and so must be reused, or is set to default, or the user will use the same pin out of convenience. For this reason, these attacks rely on user-error, which does contribute largely to MITM exploits.

Another interesting approach is the BT-Nino-MITM attack or Bluetooth No Input, No Output attack \cite{4401672}
. In this attack, the attacker forces the victim device into \textit{Just Works} mode, which does not provide any encryption or authentication. The attacker then jams the physical layer by hopping frequencies along with the victim and sends fake data. The authors also propose jamming the entire 2.4GHz frequency to for the user to try \textit{Just Works} mode.

\section{Threat Model}
TODO

@@

Jams the signal and attempts to connect using the used pin\cite{barnickel2012implementing}

jams the whole 2.4GHz frequency or frequency hops with the victim and sends fake data \cite{4401672}
